\section{Scenario for a voice-and-video-call directly between two members}
\begin{description}
 \item [INITIAL ASSUMPTION:]
  \textit{Member1 wants to start a voice-and-video-call to Member2 on his contact-list.}

 \item [NORMAL:]
  \textit{He sends a request to the other user. The other User accepts the request. The System builds a P2P
  connection between those Users. Data is exchanged via that connection. A video-chat-window and tab opens 
  on both Members platforms.}


 \item [WHAT CAN GO WRONG:]

  \textit{The request is not sent or not received.Give feedback to Member1.\newline
  The Member1 is blocked by Member2.Give feedback to Member1 (Member2 blocked you) \newline
  The connection collapses.Give feedback to Member1 and Member2 (connection timeout)}

 \item [OTHER ACTIVITIES:]
  \textit{There may not be more than one video-call to a single Member at the same time.}

 \item [SYSTEM STATE ON COMPLETION:]
  \textit{The data-stream is stopped. The video-chat-windows and tabs close on both Members platforms. The connection is cut (cancelled).}
\end{description}

\section{Scenario for starting a conference with video, audio and whiteboard functionalities}
\begin{description}
 \item [INITIAL ASSUMPTION:]
  \textit{a member wants to start a conference with video, chat and whiteboard functionality. This member has the right to start a conference}

 \item [NORMAL:]
  \textit{the member starts a conference with the plugins he wants.\newline
He invites other people to this conference by sending them a link to the conference directly through
the system (if they're members), or through email (if not members).\newline
Each user, once he joins, will be able to see other people's chat messages and videos, and can hear their audio. He can also draw on the whiteboard.\newline
Users will see a video tab for the videos of other users, and a whiteboard tab where they can draw together.\newline
Each user can choose if he wants to share his video and audio or not.}


 \item [WHAT CAN GO WRONG:]

  \textit{A user is abusing one or more plugin
  the moderator or a sub-moderator can kick the user from the conference, or block the user from accessing the plugin(s) he's abusing.\newline
  the user doesn't have a camera, or a microphone, or both.Video and audio sharing will be disabled for that user, he'll still be able to see the others though. \newline
  A user's internet speed is too low for video streaming. The user will be given the option to disbale video streaming, or lower the quality. \newline
  A user is blocked by another. The other user will not see this user's chat messages and video, nor hear his audio.\newline
  The connection collapses
  Give feedback to all users (connection timeout)\newline
  The moderator leaves the conference. The system assigns a sub-moderator as the current moderator, if at least one sub-moderator exists. If not, then some other member will be randomly assigned as moderator.\newline
  The server is overloaded. Show a message to the users, that they should expect issues because of overload.\newline}

 \item [OTHER ACTIVITIES:]
  \textit{Each user can take part in other conferences, but will have his audio and video disabled.}

 \item [SYSTEM STATE ON COMPLETION:]
  \textit{The conference is stopped. All the tabs close on all users' platforms. The connection is cut (cancelled).}
\end{description}

